Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Put \cite for Haddock back to where it was before
This is not ideal, but it as least works.
adding explanation for placeholders.
footnote for hspec-discover.
adding a comment on citation.
Incorporated suggestions made by @kazu into "Problem" section

We made two observations:
\begin{enumerate}
    \item
        Parts of a specification can be useful as user documentation.
    \item
        Doctest, a tool inspired by a Python module with the same
        name~\cite{doctest}, already allows to verify
        \emph{interactive examples} in Haddock~\cite{haddock} comments.
\end{enumerate}

@@

Hspec can be used to document the behavior of a system in a way that
is similar to a specification.  All facets of the system should be
described with evidence, including every possible corner case.

We think that some evidence is useful as user documentation, hence we
want to be able to include it in Haddock comments.  But there is also
evidence that is not useful as user documentation.  E.g. that a
particular \texttt{Monoid} instance is a monoid in the mathematical
sense is self-evident.  So we do not want to include any evidence for
that into user documentation, but we still want to automatically test
it.

@@

\begin{quote}
kazu: I'm uncomfortable with the three paragraphs above. I would change these
as follows:

We think that some evidence is useful as user documentation, hence we
want to be able to include it in Haddock comments.  But others are not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.
They should be included in code document. Both kinds of evidence
should be automatically tested.

We propose to use Doctest and Haddock for evidence that is useful as
user documentation, and Hspec for evidence that is not useful as user
documentation. The following subsections disccuss problems when
we try to carry out our proposal of BDD.
\end{quote}

@@

Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
For instance, some packages, including {\tt containers}, {\tt filepath}, 
{\tt bytestring} and {\tt text}, adopt this style.
Here is an example from the first one.

>>>>

\begin{quote}
    \emph{kazu: we should talk about Python's doctest,
    Haskell's doctest and Haddock here and put
    citation on them.}
\end{quote}

We made two observations:
\begin{enumerate}
    \item
        Parts of a specification can be useful as user documentation.
    \item
        Doctest, a tool inspired by a Python module with the same
        name~\cite{doctest}, already allows to verify
        \emph{interactive examples} in Haddock comments.
\end{enumerate}

@@

We think that some evidence is useful as user documentation.
But there is also evidence, that is not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.

@@

\begin{quote}
    TBD: Not correct English, so we have to find an other way to say
    this.

    The following subsections disccuss problems when we try to carry
    out our proposal of BDD.
\end{quote}

@@

Haddock has markup support for code blocks~\cite{haddock}.  And it is widely used to
include properties and examples in documentation.
For instance, some packages, including {\tt containers}, {\tt filepath}, 
{\tt bytestring} and {\tt text}, adopt this style.
Here is an example from the first one.
